---
title: "A Comparison of the Fuel Efficiency of Auto-transmission and Manual transmissoin Cars"
author: "Ivan Chow"
date: "8/2/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Executive Summary

This report looks at a data set of a collection of cars and explores the relationship between a set of variables and miles per gallon (MPG) (outcome). The question to be answered based on the data analysis is:

      “Is an automatic or manual transmission better for MPG”

The data sets used is the mtcars dataset provided in the CRAN Project/ R stuido.  The conclusion is:

      “Cars with manual transmission has a better MPG over automatic transmission with 24.39 MPG and 17.14 MPG respectively.”
   
Details of the quantative analyses for supporting the conclusion is provided in the following sections.

(Note: This PDF file is generated from Knitr using a R mark down file.  See the link below:

https://github.com/ivanchow/jhurmwk4/blob/master/jhurmwk4.Rmd  )

### Exploratory Data Analysis
```{r, warning=FALSE, message=FALSE}
library(dplyr)
mtcars2 <- mtcars
mtcars2$am <- as.factor(mtcars2$am)
levels(mtcars2$am) <- c("Automatic", "Manual")
```
An exploratory data analysis finds the means of MPG for auto-transmission and manual in the dataset are 24.39 MPG and 17.14 MPG respectively.

```{r}
mpg_by_am <- aggregate(mpg ~ am, data = mtcars2, mean)
mpg_by_am
```

See appendix [Exploratory Summary of the dataset and Box Plots]

### Statistial Signifance
Setting the null hypothesis as the two MPG means are not significant different, with the use of t.test(), it was the calculated p-value is 0.001374.  The low p-vlaue, < 0.01, led to the rejection of the null hypothesis. That is, the two MPG means are significant different.
See appendix [Statistial Signifance t.test output]

### Single Variable Regression Model
With single variable am, the mpg for auto transmission is 17.15 and would increase by 7.24 when changing to manual.  See appendix [Single Variable Regresssion Model Plot]

### Multivariable Regression Models
With the rest of the variables added to the model, it increases the R squared to 86.9%, which shows that we can explain a high proportion of the variance in miles per gallon. In this multivariate regression model, the effect of transmission type is smaller, as it contributes an increase of only 2.52 mpg.

An ANOVA analysis has a P-value of 1.779e-05, so we can reject the hypothesis that the multivariable regression analysis is the same as the single variale regression analysis.

The residuals are normally distributed and not heteroskedastic as shown in the plots.

See appendix [Multivariable Regresssion Model Plot]

## Appendix - Plots of the data analysis

### Exploratory Summary of the dataset and Box Plots
    
```{r mtcars}
head(mtcars)
```

```{r}
boxplot(mpg ~ am, data = mtcars2, xlab = "Transmission", 
        ylab = "Miles per gallon", main = "Fuel economy by Transmission Type")
```

### Statistial Signifance t.test output
```{r}
t.test(mtcars[mtcars2$am == "Manual",]$mpg, 
       mtcars[mtcars2$am == "Automatic",]$mpg,
       paired = FALSE, var.equal = FALSE)
```


### Single Variable Regresssion Model Plot

```{r}
fit0<-lm(mtcars$mpg~mtcars$am)
summary(fit0)$adj.r.squared
```

```{r}
summary(fit0)$coefficients
```

### Multivariable Regresssion Model Plot

```{r}
fit1<-lm(mpg~cyl+disp+hp+drat+wt+qsec+factor(vs)+factor(am)+gear+carb,data = mtcars)
summary(fit1)
```


```{r}
anova(fit0,fit1)
```


```{r}
par(mfrow=c(2,2))
plot(fit1)
```



 

