---
title: "Johns Hopkins - Regression Models Course Project - Week 4"
author: "Ivan Chow"
date: "8/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Executive Summary

Link to the Rmd file which generates this PDF file.


## Appendix - Figures


## Attachments

### Objective

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

    “Is an automatic or manual transmission better for MPG”
    "Quantify the MPG difference between automatic and manual transmissions" 
    
```{r mtcars}
summary(mtcars)
```

### Grading Criteria

   1. Did the student interpret the coefficients correctly?
   1. Did the student do some exploratory data analyses?
   1. Did the student fit multiple models and detail their strategy for model selection?
   1.  Did the student answer the questions of interest or detail why the question(s) is (are) not answerable?
   1. Did the student do a residual plot and some diagnostics?
   1. Did the student quantify the uncertainty in their conclusions and/or perform an inference correctly?
   1. Was the report brief (about 2 pages long) for the main body of the report and no longer than 5 with supporting appendix of figures?
   1. Did the report include an executive summary?
   1. Was the report done in Rmd (knitr)? 

 

